\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.75in]{geometry}


\titleformat{\section}
{}
{}
{0em}
{\large\bfseries}[\titlerule]

\renewcommand{\maketitle}{
	\begin{center}
		{\huge\bfseries
		\theauthor}
		
		\vspace{.25em}
		
		Wyatt\_Snyder@baylor.edu --- 405-625-2027
	\end{center}
}

\begin{document}
\pagenumbering{gobble}
\titleformat{\subsubsection}[runin]{\bfseries}{}{0em}{\hspace{0.15in}}[$~$---$~$]
\titlespacing{\subsubsection}{0em}{0em}{0em} 

\titleformat{\subsection}[runin]
{}
{}
{0em}
{\bfseries}
	
\title{R\'esum\'e}
\author{Wyatt Snyder}

\maketitle

\section{Education}

\subsection{Baylor University}

\subsubsection{Major}
Computer Science
\hfill
\textit{Expected Graduation}
\subsubsection{Secondary Major}
Mathematics 
\hfill
\textit{December, 2019}
\subsubsection{GPA}
3.59
\subsubsection{Relevant Coursework}
Data Structures, Systems Programming, Introduction to Computer Systems, Intro to Algorithms, Database Design, Software Engineering I, Intro to Java, Data Communications,

\section{Experience}

\subsection{Accio Data, Computer Science Intern}
\hfill\textit{June 2018 - August 2018}

\begin{itemize}
	\itemsep0em
	\item Modified company's dynamic and static web pages to create a more
	mobile-friendly experience.
	\item Created automated testing via Cypress for various web pages
	throughout the website.
	\item Implemented responsive design to a legacy code base, working with
	back-end logic to re-factor sections of the code to be more
	readable and understandable.  
\end{itemize}

\subsection{Baylor University, Student Athlete Tutor} 
\hfill\textit{August 2017 - Present}

\begin{itemize}
	\itemsep0em
	\item Assisted student athletes in their academics by strengthening their understanding of subject material in topics of computer science and mathematics.
	
	\item Worked with individual students throughout the semester. 
\end{itemize}

\subsection{LightSys, Code-a-thon Mission Trip}
\hfill
\textit{Spring Break 2017}

\begin{itemize}
	\itemsep0em
	\item Worked on a team to design an android app that would send prayer requests
	to missionaries in persecuted countries. 

	\item Set the foundation for the app by using software engineering practices such as analysis and design, implementing use cases and sequence diagram models.
\end{itemize}
  
\subsection{Additional Employment}
\begin{itemize}
	\itemsep0em
	\item Waiter at Pelicans restaurant \hfill\textit{March-July 2016, June-July 2017} 
	
	\item STEM Tutor at Rose State College \hfill\textit{September 2015 - July 2016, June-July 2017} 
	
	\item Private Piano Instructor \hfill\textit{March 2015 - July 2016}
\end{itemize}

\section{Technical skills}

\subsection{Programming}

C++, C, Java, Ruby, MySQL, {\LaTeX}, HTML, CSS, Git, Perforce

\section{Leadership and Organizations}
Eagle Scout, ACM, Upsilon Pi Epsilon 
\subsection{Co-Founder and President of The Unicycling Academy}
\begin{itemize}
	\itemsep0em
	\item Worked with vice-president to organize and oversee weekly meetings. 
	\item Taught members how to ride a unicycle, and guided them in practice.
\end{itemize}
\noindent

\end{document}


